---
title: "A User’s Guide to Network Analysis in R"
output: html_notebook
---

# Charpter 2

## Simple Visualization

```{r}
if (!require("pacman")) install.packages("pacman") # `pacman`用於確認套件是否安裝
pacman::p_load(statnet, UserNetR)
data(Moreno)
gender <- Moreno %v% "gender"
plot(Moreno, vertex.col = gender + 2, vertex.cex = 1.2)
```

### Size

> The size is simply the number of members, usually called nodes, vertices or actors.

```{r}
summary(Moreno,print.adj = FALSE)
components(Moreno)
network.size(Moreno)
```

### Density

> Density is the proportion of observed ties (also called edges, arcs, or relations) in a network to the maximum number of possible ties.

**Directed Network**

$$Density = \frac{L}{k(k - 1)}$$
**Undirected Network**

$$Density = \frac{2L}{k(k - 1)}$$

```{r}
gden(Moreno)
```


### Diameter

> The diameter then for an entire network is the longest of the shortest paths across all pairs of nodes.

```{r}

lgc <- component.largest(Moreno, result = "graph")
(gd <- geodist(lgc)) ##點與點間的距離
max(gd$gdist)

```

### Clustering Coefficient

> the presence of clustering, or the tendency to formed closed triangles.

```{r}
gtrans(Moreno, mode = "graph")
```

# Network Data Management in R

```{r}
# Netwrok data
netmat1 <- rbind(c(0, 1, 1, 0, 0), c(0, 0, 1, 1, 0), c(0, 1, 0, 0, 0), 
                 c(0, 0, 0, 0, 0), c(0, 0, 1, 0, 0))
rownames(netmat1) <- c("A", "B", "C", "D", "E")
colnames(netmat1) <- c("A", "B", "C", "D", "E")
net1 <- network(netmat1, matrix.type = "adjacency")
class(net1)
summary(net1)
gplot(net1, vertex.col = 2, displaylabels = TRUE) ## `2`是紅色

as.sociomatrix(net1) ## 轉為網絡矩陣
as.matrix(net1, matrix.type = "edgelist") ## 關係list

netmat2 <- rbind(c(1, 2), c(1, 3), c(2, 3), c(2, 4), c(3, 2), c(5, 3))
net2 <- network(netmat2, matrix.type = "edgelist")
network.vertex.names(net2) <- c("A", "B", "C", "D", "E")
summary(net2)

set.vertex.attribute(net1, "gender", c("F", "F", "M", "F", "M"))
net1 %v% "alldeg" <- degree(net1) ## 給予每個vertic點度
list.vertex.attributes(net1)
summary(net1)
get.vertex.attribute(net1, "gender")
net1 %v% "alldeg"

list.edge.attributes(net1)
set.edge.attribute(net1, "rndval", runif(network.size(net1), 0, 1))
## 給予每個關係一個隨機數值
summary(net1 %e% "rndval")
summary(get.edge.attribute(net1, "rndval"))

netval1 <- rbind(c(0, 2, 3, 0, 0), c(0, 0, 3, 1, 0), c(0, 1, 0, 0, 0),
                 c(0, 0, 0, 0, 0), c(0, 0, 2, 0, 0))
netval1 <- network(netval1, matrix.type = "adjacency", ignore.eval = FALSE, names.eval = "like")
network.vertex.names(netval1) <- c("A", "B", "C", "D", "E")
list.edge.attributes(netval1)
get.edge.attribute(netval1, "like")
as.sociomatrix(netval1)
```

* `%v%` 代表了提取*vector*資料
* `network.vertex.names()` 給予vertic名稱
* `set.vertex.attribute()` 給予vertic性質
* `list.vertex.attributes` 列出所有vertic具有的性質
* `get.vertex.attribute(data, attr)` 列出各vertic具有的某性質

## Creating a Network Object in igraph
```{r}
if (require(statnet)) detach(package:statnet) 
library(igraph)

inet1 <- graph.adjacency(netmat1)
summary(inet1)

inet2 <- graph.edgelist(netmat2)
V(inet2)$name <- c("A","B","C","D","E") 
E(inet2)$val <- c(1:6)
summary(inet2)
```

* `graph.adjacency()` 製作關係資料

## Importing Network Data
### 讀取外部資料

```{r}
if (require(igraph)) detach("package:igraph", unload = TRUE)
library(statnet)

netmat3 <- rbind(c("A", "B"), c("A", "C"), c("B", "C"), c("B", "D"), c("C", "B"), 
                 c("E", "C"))
net.df <- data.frame(netmat3)
net.df
write.csv(net.df, file = "MyData.csv", row.names = FALSE)
(net.edge <- read.csv(file = "MyData.csv")) ## 讀取外部檔案
net_import <- network(net.edge, matrix.type = "edgelist")
summary(net_import)
gden(net_import)
```

### 資料處理
```{r}
## 刪除資料
data(ICTS_G10)
gden(ICTS_G10)
length(isolates(ICTS_G10))
n3 <- ICTS_G10
delete.vertices(n3, isolates(n3))  # 刪除孤立點
gden(n3)
length(isolates(n3))


# Filtering Based on Edge Values
data(DHHS)
d <- DHHS
gden(d)
op <- par(mar = rep(0, 4))
gplot(d, gmode = "graph", edge.lwd = d %e% "collab", edge.col = "grey50", vertex.col = "lightblue", 
      vertex.cex = 1, vertex.sides = 20)
par(op)
as.sociomatrix(d)[1:6, 1:6]
list.edge.attributes(d)
as.sociomatrix(d, attrname = "collab")[1:6, 1:6]
table(d %e% "collab")

(d.val <- as.sociomatrix(d, attrname = "collab"))
d.val[d.val < 3] <- 0 ## 將val小於3設為０

d.filt <- as.network(d.val, directed = FALSE, matrix.type = "a", ignore.eval = FALSE, 
                     names.eval = "collab")
summary(d.filt, print.adj = FALSE)
op <- par(mar = rep(0, 4))
gplot(d.filt, gmode = "graph", displaylabels = TRUE, vertex.col = "lightblue", vertex.cex = 1.3, 
      label.cex = 0.4, label.pos = 5, displayisolates = FALSE)

op <- par(mar = rep(0, 4))
d.val <- as.sociomatrix(d, attrname = "collab")
gplot(d.val, gmode = "graph", thresh = 2, vertex.col = "lightblue", vertex.cex = 1.3, 
      label.cex = 0.4, label.pos = 5, displayisolates = FALSE)
par(op)
```

* `isolate()` 找出孤立點
* `delete.vertices()` 刪除 vertex

### Transforming a Directed Network to a Non-directed Network
```{r}
net1mat <- symmetrize(net1, rule = "weak")
net1mat
net1symm <- network(net1mat, matrix.type = "adjacency")
network.vertex.names(net1symm) <- c("A", "B", "C", "D", "E")
```

* `symmetrize()` 將方向性平衡
  * rule:
  1. upper: Copy the upper triangle over the lower triangle
  2. lower: Copy the lower triangle over the upper triangle
  3. strong: i<->j iff i->j and i<-j (AND rule)
  4. weak: i<->j iff i->j or i<-j (OR rule


# Chapter 4
## Basic Network Plotting and Layout

```{r}
pacman::p_load(statnet, UserNetR)
data(Moreno)
op <- par(mar = rep(0, 4), mfrow = c(1, 2))
plot(Moreno, mode = "circle", vertex.cex = 1.5)
plot(Moreno, mode = "fruchtermanreingold", vertex.cex = 1.5)
par(op)

op <- par(mar = c(0, 0, 4, 0), mfrow = c(1, 2))
gplot(Moreno, gmode = "graph", mode = "random", vertex.cex = 1.5, main = "Random Layout")
gplot(Moreno, gmode = "graph", mode = "fruchtermanreingold", vertex.cex = 1.5,
      main = "Fruchterman-Reingold")
```

### Basic Plotting Algorithms and Methods
```{r}
data("Bali")
op <- par(mar = c(0, 0, 4, 0), mfrow = c(2, 3))
gplot(Bali, gmode = "graph", edge.col = "grey75", vertex.cex = 1.5, mode = "circle", 
    main = "circle")
gplot(Bali, gmode = "graph", edge.col = "grey75", vertex.cex = 1.5, mode = "eigen", 
    main = "eigen")
gplot(Bali, gmode = "graph", edge.col = "grey75", vertex.cex = 1.5, mode = "random", 
    main = "random")
gplot(Bali, gmode = "graph", edge.col = "grey75", vertex.cex = 1.5, mode = "spring", 
    main = "spring")
gplot(Bali, gmode = "graph", edge.col = "grey75", vertex.cex = 1.5, mode = "fruchtermanreingold", 
    main = "fruchtermanreingold")
gplot(Bali, gmode = "graph", edge.col = "grey75", vertex.cex = 1.5, mode = "kamadakawai", 
    main = "kamadakawai")
par(op)

## 儲存圖片參數
mycoords1 <- gplot(Bali, gmode = "graph", vertex.cex = 1.5)
mycoords2 <- mycoords1
mycoords2[, 2] <- mycoords1[, 2] * 1.5
mycoords1
mycoords2

op <- par(mar = c(4, 3, 4, 3), mfrow = c(1, 2))
gplot(Bali, gmode = "graph", coord = mycoords1, vertex.cex = 1.5, suppress.axes = FALSE, 
    ylim = c(min(mycoords2[, 2]) - 1, max(mycoords2[, 2]) + 1), main = "Original coordinates")
gplot(Bali, gmode = "graph", coord = mycoords2, vertex.cex = 1.5, suppress.axes = FALSE, 
    ylim = c(min(mycoords2[, 2]) - 1, max(mycoords2[, 2]) + 1), main = "Modified coordinates")

```

#### Network Graph Layouts Using igraph

```{r message=FALSE, warning=FALSE}
if (require(statnet)) detach(package:statnet)
library(igraph)
library(intergraph)  ## 轉為igragh
iBali <- asIgraph(Bali)  ## igraph格式
op <- par(mar = c(0, 0, 3, 0), mfrow = c(1, 3))
plot(iBali, layout = layout_in_circle, main = "Circle")
plot(iBali, layout = layout_randomly, main = "Random")
plot(iBali, layout = layout_with_kk, main = "KK")

```

# Chapter 5
## Effective Network Graphic Design

### Node Color
```{r}
data("Bali")
gplot(Bali, vertex.col = "slateblue2", gmode = "graph")
```

### 調整透明度
```{r}
ndum <- rgraph(300, tprob = 0.025, mode = "graph")
par(mar = c(0, 0, 2, 0), mfrow = c(1, 2))
gplot(ndum, gmode = "graph", vertex.cex = 2, vertex.col = rgb(0, 0, 139, maxColorValue = 255), 
    edge.col = "grey80", edge.lwd = 0.5, main = "Fully opaque")
gplot(ndum, gmode = "graph", vertex.cex = 2, vertex.col = rgb(0, 0, 139, alpha = 80, 
    maxColorValue = 255), edge.col = "grey80", edge.lwd = 0.5, main = "Partly transparent")
```
* using argument `alpha` 

### Change node Color
```{r message=FALSE, paged.print=TRUE}
if (require(igraph)) detach(package:igraph)
?(Bali)
data("Bali")
rolelab <- get.vertex.attribute(Bali, "role")  
op <- par(mar = c(0, 0, 0, 0))
plot(Bali, usearrows = FALSE, vertex.cex = 1.5, label = rolelab, displaylabels = T, 
    vertex.col = "role")

## 更改色卡
library(RColorBrewer)
display.brewer.pal(5, "Dark2")

my_pal <- brewer.pal(5, "Dark2")
rolecat <- as.factor(get.vertex.attribute(Bali, "role"))
plot(Bali, vertex.cex = 1.5, label = rolelab, displaylabels = T, vertex.col = my_pal[rolecat])
```

the Bali terrorist network has the role vertex attribute which stores the categorical description of the role that each member played in the network.
* 預設調色盤缺點
  * limited to eight colors
  * starts with black
  
### Node Shape

```{r}
op <- par(mar=c(0,0,0,0))
sidenum <- 3:7 
plot(Bali, usearrows = FALSE, vertex.cex = 4, 
     displaylabels = F, vertex.sides = sidenum[rolecat])
par(op)
```

Unfortunately, `statnet` has only a **limited ability** to distinguish nodes by shapes

### Node Size

```{r}
op <- par(mar = c(0, 0, 2, 0), mfrow = c(1, 3))
plot(Bali, vertex.cex = 0.5, main = "Too small")
plot(Bali, vertex.cex = 2, main = "Just right")
plot(Bali, vertex.cex = 6, main = "Too large")
par(op)

# using centrality as exmple
deg <- sna::degree(Bali, gmode = "graph")
op <- par(mar = c(0, 0, 2, 1), mfrow = c(1, 2))
plot(Bali, usearrows = T, vertex.cex = deg, main = "Raw")
plot(Bali, usearrows = FALSE, vertex.cex = log(deg), main = "Adjusted")
par(op)

cls <- closeness(Bali, gmode = "graph")
op <- par(mar = c(0, 0, 2, 1), mfrow = c(1, 2))
plot(Bali, usearrows = T, vertex.cex = cls, main = "Raw")
plot(Bali, usearrows = FALSE, vertex.cex = 4 * cls, main = "Adjusted")
par(op)

bet <- betweenness(Bali, gmode = "graph")
op <- par(mar = c(0, 0, 2, 1), mfrow = c(1, 2))
plot(Bali, usearrows = T, vertex.cex = bet, main = "Raw")
plot(Bali, usearrows = FALSE, vertex.cex = sqrt(bet + 1), main = "Adjusted")
```
* argument `vertex.cex`
* 調整方式：
  ** log
  ** 倍數法
  ** 開根號
  
#### creating `rescale` function

```{r}
rescale <- function(nchar,low,high) {
min_d <- min(nchar)
max_d <- max(nchar)
rscl <- ((high-low)*(nchar-min_d))/(max_d-min_d)+low 
rscl
}

plot(Bali, vertex.cex = rescale(deg, 1, 6), main = "Adjusted node sizes with rescale function.")
```

### Node Label

```{r}
get.vertex.attribute(Bali, "vertex.names")
op <- par(mar = c(0, 0, 0, 0))
plot(Bali, displaylabels = TRUE, label.cex = 0.8, pad = 0.4, label.col = "darkblue")
par(op)
rolelab <- get.vertex.attribute(Bali, "role")
plot(Bali, usearrows = FALSE, label = rolelab, displaylabels = T, label.col = "darkblue")
```

If a network object in `statnet` contains the special vertex attribute **vertex.names**, then this can be used to automatically display node labels when plotting.


### Edge Width

```{r}
op <- par(mar = c(0, 0, 0, 0))
IClevel <- Bali %e% "IC"
plot(Bali, vertex.cex = 1.5, edge.lwd = 1.5 * IClevel)
par(op)
```
* using argument `edge.lwd`

### Edge Color
```{r}
n_edge <- network.edgecount(Bali)
edge_cat <- sample(1:3, n_edge, replace = T)  ## example
linecol_pal <- c("blue", "red", "green")
plot(Bali, vertex.cex = 1.5, vertex.col = "grey25", edge.col = linecol_pal[edge_cat], 
    edge.lwd = 2)
```
* using argument `edge.col`

###  Edge Type

```{r}
n_edge <- network.edgecount(Bali)
edge_cat <- sample(1:3, n_edge, replace = T)
line_pal <- c(2, 3, 4)
gplot(Bali, vertex.cex = 0.8, gmode = "graph", vertex.col = "gray50", edge.lwd = 1.5, 
    edge.lty = line_pal[edge_cat])
```

the different line types **do not show up clearly** using `plot()`, so `gplot()` is used here
* using argument `edge.lty`

### Legends

```{r message=FALSE, warning=FALSE}
my_pal <- brewer.pal(5, "Dark2")
rolecat <- as.factor(get.vertex.attribute(Bali, "role"))
library(scales)
plot(Bali, vertex.cex = rescale(deg, 1, 5), vertex.col = my_pal[rolecat])
legend("bottomleft", legend = c("BM", "CT", "OA", "SB", "TL"), col = my_pal, pch = 19,
       pt.cex = 1.5, bty = "n", title = "Terrorist Role")
```

# Chapter 6
## Interactive Network Graphics

先跳過

# Chapter 7
## Actor Prominence

## Centrality: Prominence for Undirected Networks

### 1. Degree Centrality

>  Degree centrality is simply the degree of each node.

```{r message=FALSE, warning=FALSE, paged.print=FALSE}
net <- network(netmat1)
degree(net, gmode = "graph")
```

### 2. Closeness Centrality

>  nodes are more prominent to the extent they are close to all other nodes in the network

$$C_{c}(n_{i}) =\left [ \sum_{j = 1}^{g}d(n_{i}, n_{j}) \right ] ^{-1}$$

* where *d* is the path distance between two nodes.

```{r message=FALSE, warning=FALSE, paged.print=FALSE}
closeness(net, gmode = "graph")
```

### 3. Betweenness Centrality

> such that a path between the other nodes has to go through that node. 

$$C_{Ｂ}(n_{i}) =\sum_{j < k}g_{jk}(n_{i})/g_{jk}$$
where $g_{jk}$ is the geodesic between nodes j and k. (A geodesic is the shortest path between two nodes.) $g_{jk}(n_{i})$ is the number of geodesics between nodes j and k that contain node i.

```{r message=FALSE, warning=FALSE, paged.print=FALSE}
betweenness(net, gmode="graph")
```

### Centrality Measures in R

> ![picture](https://lh3.googleusercontent.com/KekTdJ3AVy-GzW4FUSt6OiHK6Z2fETQquHLmO-WXlGSmNN045U3-Hnis5-tuf7Q_rUjFVytvvn6M0-H40pwZ3OWC5Zb3w87L48m1tZkRzu4cxuHA4GBY07rVgNzMDYFdEGnpWgU3PYQ=w2400)

```{r}
library(statnet)
data(DHHS)
df.prom <- data.frame(deg = sna::degree(DHHS), cls = closeness(DHHS), btw = betweenness(DHHS), 
                      evc = evcent(DHHS), inf = infocent(DHHS), flb = flowbet(DHHS))
cor(df.prom) ## correlation
```

### Reporting Centrality

```{r message=FALSE, warning=FALSE}
data(Bali)
my_pal <- brewer.pal(5, "Set2")
rolecat <- Bali %v% "role"
gplot(Bali, usearrows = FALSE, displaylabels = TRUE, vertex.col = my_pal[as.factor(rolecat)], 
    edge.lwd = 0, edge.col = "grey25")
legend("topright", legend = c("BM","CT","OA","SB", "TL"), col = my_pal, pch = 19, pt.cex = 2)

data(Bali)
df.prom2 <- data.frame(degree = degree(Bali), closeness = closeness(Bali), 
                       betweenness = betweenness(Bali))
row.names(df.prom2) <- Bali %v% "vertex.names"
df.promsort <- df.prom2[order(-df.prom2$degree), ]
cd <- centralization(Bali, degree)
cc <- centralization(Bali, closeness)
cb <- centralization(Bali, betweenness)
df.promsort <- rbind(df.promsort, c(cd, cc, cb))
row.names(df.promsort)[18] <- "Centralization"
df.promsort

deg <- degree(Bali, rescale = TRUE)
op <- par(mfrow=c(1,2)) 
gplot(Bali, usearrows = FALSE, displaylabels=FALSE, vertex.cex = deg, 
      vertex.col = my_pal[as.factor(rolecat)], edge.lwd = 0, edge.col = "grey25", main = "Too small")
gplot(Bali, usearrows = FALSE, displaylabels = FALSE, 
      vertex.cex = deg*20, vertex.col =my_pal[as.factor(rolecat)], edge.lwd = 0, edge.col = "grey25", 
      main ="A little better")
par(op)

deg <- degree(Bali, rescale = TRUE) 
gplot(Bali, usearrows = FALSE, displaylabels = TRUE,
      vertex.cex = deg*12, vertex.col = my_pal[as.factor(rolecat)], edge.lwd = 0.5, 
      edge.col = "grey75")
legend("topright", legend = c("BM","CT","OA","SB","TL"), col = my_pal, pch = 19, pt.cex = 2)
```

## Cutpoints and Bridges

* using fuction `cutponts()`

# Chapter 8
## Subgroups

### Cliques

>  a subset of nodes that have all possible ties among them.

```{r message=FALSE, warning=FALSE}
if (require(statnet)) detach(package:statnet)
library(igraph)
(clqexmp <- graph.formula(A:B:C:D - -A:B:C:D, D - E, E - F - G - E))

clique.number(clqexmp)
cliques(clqexmp, min = 3)
maximal.cliques(clqexmp, min = 3)
largest.cliques(clqexmp)
V(clqexmp)[unlist(largest.cliques(clqexmp))]
```

Cliques, however, have two major **disadvantages** that reduce their utility in realworld social network analysis.
1. a clique is a very conservative definition of a cohesive subgroup.
2. they simply are not very common in larger social networks. 

### k-Cores

> each vertex is connected to at least k other vertices in the subgraph. 

* advantages
  **  nested
  **  do not overlap
  **  easy to identify
  
```{r message=FALSE, warning=FALSE}
library(statnet)
data(DHHS) 
library(intergraph) 
pacman::p_load(igraph)
iDHHS <- asIgraph(DHHS) 
graph.density(iDHHS)

iDHHS <- subgraph.edges(iDHHS, E(iDHHS)[collab > 2]) ## subgroup
graph.density(iDHHS)

coreness <- graph.coreness(iDHHS)
table(coreness) ## The results tell us the k-cores range from 1 to 6
(maxCoreness <- max(coreness))
```

```{r}
Vname <- get.vertex.attribute(iDHHS, name = "vertex.names", index = V(iDHHS))
V(iDHHS)$name <- Vname
V(iDHHS)$color <- coreness + 1
op <- par(mar = rep(0, 4))
plot(iDHHS, vertex.label.cex = 0.8) 
par(op)
```
```{r}
colors <- rainbow(maxCoreness) 
op <- par(mar = rep(0, 4)) 
plot(iDHHS, vertex.label = coreness, vertex.color = colors[coreness])
par(op)
```

#### in different k-core
```{r message=FALSE, warning=FALSE}
V(iDHHS)$name <- coreness
V(iDHHS)$color <- colors[coreness]
iDHHS1_6 <- iDHHS
iDHHS2_6 <- induced.subgraph(iDHHS, vids = which(coreness > 1))
iDHHS3_6 <- induced.subgraph(iDHHS, vids = which(coreness > 2))
iDHHS4_6 <- induced.subgraph(iDHHS, vids = which(coreness > 3))
iDHHS5_6 <- induced.subgraph(iDHHS, vids = which(coreness > 4))
iDHHS6_6 <- induced.subgraph(iDHHS, vids = which(coreness > 5))

lay <- layout.fruchterman.reingold(iDHHS)
op <- par(mfrow = c(3, 2), mar = c(3, 0, 2, 0))
plot(iDHHS1_6, layout = lay, main = "All k-cores")
plot(iDHHS2_6, layout = lay[which(coreness > 1), ], main = "k-cores 2-6")
plot(iDHHS3_6, layout = lay[which(coreness > 2), ], main = "k-cores 3-6")
plot(iDHHS4_6, layout = lay[which(coreness > 3), ], main = "k-cores 4-6")
plot(iDHHS5_6, layout = lay[which(coreness > 4), ], main = "k-cores 5-6")
par(op)
```

* `induced.subgraph()` 選取次群體

### Modularity

> Modularity is a measure of the structure of the network, specifically the extent to which nodes exhibit clustering where there is greater density within the clusters and less density between them.

#### 分組示意圖
```{r warning=FALSE}
g1 <- graph.formula(A - B - C - A, D - E - F - D, G - H - I - G, A - D - G - A)
V(g1)$grp_good <- c(1, 1, 1, 2, 2, 2, 3, 3, 3)
V(g1)$grp_bad <- c(1, 2, 3, 2, 3, 1, 3, 1, 2)
op <- par(mfrow = c(1, 2))
plot(g1, vertex.color = (V(g1)$grp_good), vertex.size = 20, main = "Good Grouping")
plot(g1, vertex.color = (V(g1)$grp_bad), vertex.size = 20, main = "Bad Grouping")
par(op)

modularity(g1, V(g1)$grp_good)
modularity(g1, V(g1)$grp_bad)

```

```{r}
library(intergraph) 
data(DHHS)
iDHHS <- asIgraph(DHHS) 
table(V(iDHHS)$agency)
V(iDHHS)[1:10]$agency
modularity(iDHHS,(V(iDHHS)$agency+1)) ## agency is numbered starting at 0 so we add 1

```
可以用此算出次群體內的密度，例如，性別分群後群體的密度為何。

#### Community Detection Algorithms

```{r}
iMoreno <- asIgraph(Moreno)
cw <- cluster_walktrap(iMoreno) 
membership(cw)
modularity(cw)
plot(cw, iMoreno) 
```
Modularity is fairly high, suggesting that the walktrap algorithm has **done a good job** at detecting subgroup structure.

```{r}
data(Bali)
iBali <- asIgraph(Bali)

cw <- cluster_walktrap(iBali)
modularity(cw)
membership(cw)

ceb <- cluster_edge_betweenness(iBali)
modularity(ceb)
membership(ceb)

cs <- cluster_spinglass(iBali) 
modularity(cs)
membership(cs)

cfg <- cluster_fast_greedy(iBali)
modularity(cfg)
membership(cfg)

clp <- cluster_label_prop(iBali) 
modularity(clp)
membership(clp)

cle <- cluster_leading_eigen(iBali)
modularity(cle)
membership(cle)

cl <- cluster_louvain(iBali) 
modularity(cl)
membership(cl)

```

These results show that all the detection algorithms identify either two or three subgroups. Modularity ranges from about 0.24 to 0.30.

```{r}
table(V(iBali)$role, membership(cw))
compare(as.numeric(factor(V(iBali)$role)), cw, method = "adjusted.rand")
compare(cw, ceb, method = "adjusted.rand")
compare(cw, cs, method = "adjusted.rand")
compare(cw, cfg, method = "adjusted.rand")

op <- par(mfrow = c(3, 2), mar = c(3, 0, 2, 0))
plot(ceb, iBali, vertex.label = V(iBali)$role, main = "Edge Betweenness")
plot(cfg, iBali, vertex.label = V(iBali)$role, main = "Fastgreedy")
plot(clp, iBali, vertex.label = V(iBali)$role, main = "Label Propagation")
plot(cle, iBali, vertex.label = V(iBali)$role, main = "Leading Eigenvector")
plot(cs, iBali, vertex.label = V(iBali)$role, main = "Spinglass")
par(op)
```

* `compare` assesses the distance between two community structures.

# Chapter 9
## Affiliation Networks

### Affiliations as 2-Mode Networks

```{r}
C1 <- c(1, 1, 1, 0, 0, 0)
C2 <- c(0, 1, 1, 1, 0, 0)
C3 <- c(0, 0, 1, 1, 1, 0)
C4 <- c(0, 0, 0, 0, 1, 1)
aff.df <- data.frame(C1, C2, C3, C4)
row.names(aff.df) <- c("S1", "S2", "S3", "S4", "S5", "S6")
aff.df
```
>> Students grouped by classes
 
This type of data matrix is called an incidence matrix, and it depicts how n actors belong to g groups.

### Bipartite Graphs

there are always two types of nodes: one type for the actors, and another type for the groups or events to which the actors belong.

```{r}
library(igraph)
bn <- graph.incidence(aff.df)

plt.x <- c(rep(2, 6), rep(4, 4))
plt.y <- c(7:2, 6:3)
lay <- as.matrix(cbind(plt.x, plt.y))

shapes <- c("circle","square")
colors <- c("blue","red") 
plot(bn, vertex.color = colors[V(bn)$type + 1], vertex.shape = shapes[V(bn)$type + 1],
     vertex.size = 10, vertex.label.degree = -pi/2, 
     vertex.label.dist = 1.2, vertex.label.cex = 0.9, layout = lay)
```

```{r}
get.incidence(bn)
V(bn)$type
V(bn)$name
```
all the students have type = FALSE, and the class nodes have type = TRUE.

### Creating Affiliation Networks from Edge Lists in `igraph`

```{r}
(el.df <- data.frame(rbind(c("S1", "C1"), c("S2", "C1"), c("S2", "C2"), c("S3", "C1"),  
                          c("S3", "C2"), c("S3", "C3"), c("S4", "C2"), c("S4", "C3"),  
                          c("S5", "C3"), c("S5", "C4"), c("S6", "C5"))))
(bn2 <- graph.data.frame(el.df, directed = F))
V(bn2)$type <- V(bn2)$name %in% el.df[, 1] ## set bipartite graph.
bn2
graph.density(bn) == graph.density(bn2) ## 證明與前者相同

shapes <- c("circle", "square")
colors <- c("blue", "red") 
plot(bn, vertex.color = colors[V(bn)$type + 1], vertex.shape = shapes[V(bn)$type + 1],
     vertex.size = 10, vertex.label.degree = -pi/2, vertex.label.dist = 1.2,
     vertex.label.cex = 0.9)
```
Note that 1 is added to type index because as a logical vector it starts at 0, whereas we want to select either the first or second elements of the shapes/colors vectors.

### Projections
```{r}
(bn.pr <- bipartite_projection(bn))
graph.density(bn.pr$proj1) ## first mode

bn.student <- bn.pr$proj1
bn.class <- bn.pr$proj2 
graph.density(bn.student)

get.adjacency(bn.student, sparse = F, attr = "weight")
get.adjacency(bn.class, sparse = F, attr = "weight")

```

* `bipartite_projection()` 
1. first network is made up of the direct ties among the first mode (in our case students), 
2. the second network shows the ties among the second mode (classes).


```{r}
shapes <- c("circle", "square")
colors <- c("blue", "red")
op <- par(mfrow = c(1, 2))
plot(bn.student, vertex.color = "blue", vertex.shape = "circle", main = "Students", 
    edge.width = E(bn.student)$weight * 2, vertex.size = 15, vertex.label.degree = -pi/2, 
    vertex.label.dist = 1.2, vertex.label.cex = 1)
plot(bn.class, vertex.color = "red", vertex.shape = "square", main = "Classes", 
     edge.width = E(bn.student)$weight * 2, vertex.size = 15, vertex.label.degree = -pi/2,
     vertex.label.dist = 1.2, vertex.label.cex = 1)
```

## Example: Hollywood Actors as an Affiliation Network
```{r}
data(hwd)
(h1 <- hwd )

# 資料探索
V(h1)$name[1:10]
V(h1)$type[1:10]
V(h1)$IMDBrating[1:10]

V(h1)$shape <- ifelse(V(h1)$type == T, "square", "circle")
V(h1)$shape[1: 10]
V(h1)$color <- ifelse(V(h1)$type == T, "red", "lightblue")

h2 <- subgraph.edges(h1, E(h1)[inc(V(h1)[name %in% c("The Wolf of Wall Street", "Gangs of New York",
"The Departed")])])

plot(h2, layout = layout_with_kk)
```
 * `inc` function takes a vertex sequence as an argument, and returns the incident edges.
  >  special function of the E() edge iterator.

#### descriptive statistics
```{r}
graph.density(h1)
table(degree(h1, v = V(h1)[type == F]))
mean(degree(h1, v = V(h1)[type == F]))
```

```{r}
V(h1)$deg <- degree(h1)
V(h1)[type==FALSE & deg > 4]$name ## 中心度高的演員
busy_actor <- data.frame(cbind(
  Actor = V(h1)[type == F & deg > 4]$name, 
  Movies = V(h1)[type == F & deg > 4]$deg 
))
busy_actor[order(busy_actor$Movies,decreasing = TRUE), ]

for (i in 161:1365) {
  V(h1)[i]$totrating <- sum(V(h1)[nei(i)]$IMDBrating)
}
```

